A Linear Solution of the Linearity Challenge

### 2025-12-24 paper/abstract.tex
revised abstract

\abstract{%
    We describe an Agda formalisation of a process calculus based on classical
    linear logic that supports the modeling of binary sessions. The
    formalisation turns out to be remarkably compact despite the use of
    ``plain'' context splitting for the handling of linear resources. We argue
    that the logical nature of the calculus and the use of explicit
    continuations contribute to the simplicity of its formalisation.
    %
}

>>>>

\abstract{%
    We describe the Agda formalisation of a process calculus based on classical
    linear logic that supports the modeling of binary sessions. The
    formalisation turns out to be remarkably compact despite the use of
    ``plain'' context splitting for the proper management of linear channels. We
    argue that the logical nature of the calculus and the use of explicit
    continuations are contributing factors to the simplicity of its
    formalisation.
    %
}
